\newcommand*\name{Anurag Kushawaha}
\newcommand*\email{anurag.kushwaha365@gmail.com}
\newcommand*\phone{+91-8011764653}
\newcommand*\website{anuragkush.dev}
\newcommand*\github{4nuragk}
\newcommand*\linkedin{anurag-cser}

\newcommand*\recipientfirstname{\empty}
\newcommand*\recipientlastname{\empty}
\newcommand*\recipientprefix{\empty}
\newcommand*\recipienttitle{\empty}
\newcommand*\company{JPMorgan Chase \& Co.}
\newcommand*\companyaddress{Hyderabad}
\newcommand*\companycity{Telangana, India}
\newcommand*\companystate{}
\newcommand*\companyzipcode{500081}

\newcommand*\letter{
    This letter is to express my interest in your Software Engineering position.
    
    Some background - I’m currently working as Asst. Project Engineer at IIT Guwahati. The project is funded by MeiTy. I have a Bachelor's in Technology degree in Computer Science \& Engineering branch.
    
    I’m excited to apply for the Software Engineering position at JPMorgan Chase & Co. Although I’m an entry-level applicant, I have 1+ years of experience in software development. I am passionate about doing a great job and out of the skills you’re looking for I have already developed skills like solving problems, software development and Big Data. I believe I’ll make an excellent Software Engineer thanks to my experience \& skills.
    
    I’m excited to show you how my skills can help you achieve your upcoming goals.
    
    Please feel free to refer to my CV links for examples of skills and
    development work.
    
    I look forward to hearing back! \\
    
    
    
}